---
title: "healthRecSys data analysis subjective eval"
output: html_document
---

# Set up

Set working directory and load the data. Filter out data from Prolific.
```{r ggpubr}
setwd("/Users/lucileca/Desktop/Conversational_Agent/server_side/food/resources/data_collection/healthRecSys")
##library(ggpubr)
data_star_eval <- read.csv("starEval_all.csv")
```

Libraries
```{r}
library(ggplot2)
library(ggpubr)
library(tidyr)
library(plyr)
library(dplyr)
library(magrittr)
library(car)
library(lsmeans)
library(ggpubr)
```

Check the data
```{r}
View(data_star_eval)
```

Create groups for Tags-Mode and Reco-Mode conditions
```{r}
data_star_eval$tags_mode <- ifelse((data_star_eval$file=="s_p_pref" | data_star_eval$file=="s_p_health" | data_star_eval$file=="s_p_hybrid"), 'no-tags', 'tags')
data_star_eval$reco_mode <- ifelse((data_star_eval$file=="s_p_pref" | data_star_eval$file=="s_p_pref_wtags"), 'pref', ifelse((data_star_eval$file=="s_p_health" | data_star_eval$file=="s_p_health_wtags"), 'health', 'hybrid'))


data_no_tags <- subset(data_star_eval, tags_mode == "no-tags")
data_tags <- subset(data_star_eval, tags_mode == "tags")
```

Number of data points per condition
```{r}
aggregate(cbind(count = file) ~ file, 
          data = data_star_eval, 
          FUN = function(x){NROW(x)})
```

# Demographics

Age
```{r}
data_star_eval_age <- data_star_eval["age"]
data_star_eval_long <- gather(data_star_eval_age, factor_key=TRUE)
data_star_eval_long%>% group_by(key)%>%
  summarise(mean= mean(value), 
            sd= sd(value), 
            max = max(value),
            min = min(value), 
            upperQ = quantile(value,0.75),
            lowerQ = quantile(value,0.25))
```

Number of male / female
```{r}
gender_data_star_eval <- aggregate(cbind(count = gender) ~ gender, 
          data = data_star_eval, 
          FUN = function(x){NROW(x)})

ddply(gender_data_star_eval, .(), mutate, pct = count / sum(count) * 100)
```

Employment category
```{r}
employment_data_star_eval <- aggregate(cbind(count = employment) ~ employment, 
          data = data_star_eval, 
          FUN = function(x){NROW(x)})

ddply(employment_data_star_eval, .(), mutate, pct = count / sum(count) * 100)
```

Education level
```{r}
education_data_star_eval <- aggregate(cbind(count = education) ~ education, 
          data = data_star_eval, 
          FUN = function(x){NROW(x)})

ddply(education_data_star_eval, .(), mutate, pct = count / sum(count) * 100)
```

# Plots

Plot user ratings for Reco-Mode and Tags-Mode
```{r}
ggplot(data=data_star_eval, aes(x=tags_mode, y=ratings.avg)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)
ggplot(data=data_star_eval, aes(x=reco_mode, y=ratings.avg)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)
```

Plot ratings averages for all conditions
```{r}
ggplot(data=data_star_eval, aes(x=file, y=ratings.avg)) + geom_boxplot() +
  stat_summary(fun.y=mean, colour="darkred", geom="point", 
               shape=18, size=3,show.legend = FALSE)
```

# Analysis 

## Checking for main effect of Tags-Mode and Reco-Mode + interaction

ANOVA for recipe ratings
```{r}
model_star_eval = lm(ratings.avg ~ tags_mode + reco_mode + tags_mode:reco_mode, data = data_star_eval)
print(Anova(model_star_eval, type = 'II'))
```

## When Tags-Mode = no-tags, cheking for main effect of Reco-Mode
ANOVA for recipe ratings
```{r}
model_no_tags = lm(ratings.avg ~ reco_mode, data = data_no_tags)
print(Anova(model_no_tags, type = 'II'))
```

## When Tags-Mode = tags, cheking for main effect of Reco-Mode
ANOVA for recipe ratings
```{r}
model_tags = lm(ratings.avg ~ reco_mode, data = data_tags)
print(Anova(model_tags, type = 'II'))
```

# Interaction plot

```{r}
interaction.plot(x.factor     = data_star_eval$tags_mode,
                 trace.factor = data_star_eval$reco_mode,
                 response     = data_star_eval$ratings.avg,
                 fun = mean,
                 type="b",
                 col=c("black","red","green"),  ##  Colors for levels of trace var.
                 pch=c(19, 17, 15),             ##  Symbols for levels of trace var.
                 fixed=TRUE,                    ##  Order by factor order in data
                 leg.bty = "o",
                 xlab = "Reco-Mode",
                 ylab = "Ratings Averages",
                 #ylim = c(3.7,4.9),
                 trace.label = "Tag-Mode")

```


