---
title: "healthRecSys mydata analysis objective eval"
output:
  html_document:
    toc: true
    theme: united
---

# Set up

Set working directory and load the mydata. Filter out mydata from Prolific.
```{r ggpubr}
setwd("/Users/lucileca/Desktop/Conversational_Agent/server_side/food/resources/data_collection/healthRecSys")
##library(ggpubr)
mydata <- read.csv("all.csv")
mydata_reco_health_scores <- read.csv("reco_health_scores.csv")
```

Libraries
```{r}
library(ggplot2)
library(ggpubr)
library(tidyr)
library(plyr)
library(dplyr)
library(magrittr)
library(car)
library(lsmeans)
library(ggpubr)
```

Check the mydata
```{r}
View(mydata)
View(mydata_reco_health_scores)
```

Create groups for Tags-Mode and Reco-Mode conditions
```{r}
mydata$tags_mode <- ifelse((mydata$cond=="cond_pref" | mydata$cond=="cond_health" | mydata$cond=="cond_hybrid"), 'no-tags', 'tags')
mydata$reco_mode <- ifelse((mydata$cond=="cond_pref" | mydata$cond=="cond_pref_with_tags"), 'pref', ifelse((mydata$cond=="cond_health" | mydata$cond=="cond_health_with_tags"), 'health', 'hybrid'))

mydata_no_tags <- subset(mydata, tags_mode == "no-tags")
mydata_tags <- subset(mydata, tags_mode == "tags")

attach(mydata)
df_tags <- mydata[which(tags_mode=="tags"),]
detach(mydata)
```

Number of mydata points per condition
```{r}
aggregate(cbind(count = cond) ~ cond, 
          data = mydata, 
          FUN = function(x){NROW(x)})
```

# Demographics

Duration
```{r}
mydata_age <- mydata["duration_sec"]
mydata_long <- gather(mydata_age, factor_key=TRUE)
mydata_long%>% group_by(key)%>%
  summarise(mean= mean(value), 
            sd= sd(value), 
            max = max(value),
            min = min(value), 
            upperQ = quantile(value,0.75),
            lowerQ = quantile(value,0.25))
```
Duration AMT
```{r}
mydata_age <- mydata["duration_AMT_sec"]
mydata_long <- gather(mydata_age, factor_key=TRUE)
mydata_long%>% group_by(key)%>%
  summarise(mean= mean(value), 
            sd= sd(value), 
            max = max(value),
            min = min(value))
```

Age
```{r}
mydata_age <- mydata["age"]
mydata_long <- gather(mydata_age, factor_key=TRUE)
mydata_long%>% group_by(key)%>%
  summarise(mean= mean(value), 
            sd= sd(value), 
            max = max(value),
            min = min(value), 
            upperQ = quantile(value,0.75),
            lowerQ = quantile(value,0.25))
```

Number of male / female
```{r}
gender_mydata <- aggregate(cbind(count = gender) ~ gender, 
          data = mydata, 
          FUN = function(x){NROW(x)})

ddply(gender_mydata, .(), mutate, pct = count / sum(count) * 100)
```

Employment category
```{r}
employment_mydata <- aggregate(cbind(count = employment) ~ employment, 
          data = mydata, 
          FUN = function(x){NROW(x)})

ddply(employment_mydata, .(), mutate, pct = count / sum(count) * 100)
```

Education level
```{r}
education_mydata <- aggregate(cbind(count = education) ~ education, 
          data = mydata, 
          FUN = function(x){NROW(x)})

ddply(education_mydata, .(), mutate, pct = count / sum(count) * 100)
```

Participants who said they are influenced by the health tag
```{r}
healthInfluence_mydata <- aggregate(cbind(count = health_influence) ~ health_influence, 
          data = mydata, 
          FUN = function(x){NROW(x)})

ddply(healthInfluence_mydata, .(), mutate, pct = count / sum(count) * 100)

healthInfluence_mydata <- aggregate(cbind(count = health_influence) ~ health_influence, 
          data = df_tags, 
          FUN = function(x){NROW(x)})

ddply(healthInfluence_mydata, .(), mutate, pct = count / sum(count) * 100)
```

Participants who say healthiness info is important
```{r}
tmp_mydata <- aggregate(cbind(count = health_important_str) ~ health_important_str, 
          data = mydata, 
          FUN = function(x){NROW(x)})

ddply(tmp_mydata, .(), mutate, pct = count / sum(count) * 100)
```


# Pilot exploration

Mean of health values of recommended recipes for hybrid pilots and mean of f1
```{r}
aggregate(mydata[, "reco.health.score"], list(mydata$file), mean)
aggregate(mydata[, "f1"], list(mydata$file), mean)
```

Median of health values of recommended recipes for hybrid pilots
```{r}
aggregate(mydata_reco_health_scores[, "reco.health.score"], list(mydata_reco_health_scores$file), mean)
aggregate(mydata_reco_health_scores[, "reco.health.score"], list(mydata_reco_health_scores$file), median)
```

Get most commun element
```{r}
as.table(with(mydata_reco_health_scores,by(reco.health.score,file,function(xx)names(which.max(table(xx))))))
```


Plot F1, HealthScore (eval) and Satisfaction for all conditions we tried in pilot
```{r}
ggplot(data=mydata, aes(x=file, y=health.score.eval)) + geom_boxplot() +
  stat_summary(fun.y=mean, colour="darkred", geom="point", 
               shape=18, size=3,show.legend = FALSE) 

ggplot(data=mydata, aes(x=file, y=AUC)) + geom_boxplot() +
  stat_summary(fun.y=mean, colour="darkred", geom="point", 
               shape=18, size=3,show.legend = FALSE) 

ggplot(data=mydata, aes(x=file, y=f1)) + geom_boxplot() +
  stat_summary(fun.y=mean, colour="darkred", geom="point", 
               shape=18, size=3,show.legend = FALSE) 

ggplot(data=mydata, aes(x=file, y=reco.health.score)) + geom_boxplot() +
  stat_summary(fun.y=mean, colour="darkred", geom="point", 
               shape=18, size=3,show.legend = FALSE) 

```

# Descriptive stats

F1
```{r}
ddply(mydata,~cond,summarise,mean=mean(f1),sd=sd(f1))
ddply(mydata,~reco_mode,summarise,mean=mean(f1),sd=sd(f1))
ddply(mydata,~tags_mode,summarise,mean=mean(f1),sd=sd(f1))
```

Health score (eval)
```{r}
ddply(mydata,~cond,summarise,mean=mean(health.score.eval),sd=sd(health.score.eval))
ddply(mydata,~reco_mode,summarise,mean=mean(health.score.eval),sd=sd(health.score.eval))
ddply(mydata,~tags_mode,summarise,mean=mean(health.score.eval),sd=sd(health.score.eval))
```

Satisfaction
```{r}
ddply(mydata,~cond,summarise,mean=mean(satisfaction),sd=sd(satisfaction))
ddply(mydata,~reco_mode,summarise,mean=mean(satisfaction),sd=sd(satisfaction))
ddply(mydata,~tags_mode,summarise,mean=mean(satisfaction),sd=sd(satisfaction))
```

Easiness
```{r}
ddply(mydata,~cond,summarise,mean=mean(easiness),sd=sd(easiness))
ddply(mydata,~reco_mode,summarise,mean=mean(easiness),sd=sd(easiness))
ddply(mydata,~tags_mode,summarise,mean=mean(easiness),sd=sd(easiness))
```

# Plots

Plot F1, HealthScore (eval) and Satisfaction for Tags-Mode (tags VS no-tags)
```{r}
# ggboxplot(mydata, x = "tags_mode", y = "f1", ylab = "F1")
ggplot(data=mydata, aes(x=tags_mode, y=f1)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)
ggplot(data=mydata, aes(x=tags_mode, y=health.score.eval)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)
ggplot(data=mydata, aes(x=tags_mode, y=satisfaction)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)
# ggboxplot(mydata, x = "tags_mode", y = "health.score.eval", ylab = "HealthScore (eval)")
# ggboxplot(mydata, x = "tags_mode", y = "satisfaction", ylab = "Satisfaction")
```

Plot F1, HealthScore (eval) and Satisfaction for Reco-Mode (pref vs health vs hybrid)
```{r}
ggplot(data=mydata, aes(x=reco_mode, y=f1)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)
ggplot(data=mydata, aes(x=reco_mode, y=health.score.eval)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)
ggplot(data=mydata, aes(x=reco_mode, y=satisfaction)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)
# ggboxplot(mydata, x = "reco_mode", y = "f1", ylab = "F1")
# ggboxplot(mydata, x = "reco_mode", y = "health.score.eval", ylab = "HealthScore (eval)")
# ggboxplot(mydata, x = "reco_mode", y = "satisfaction", ylab = "Satisfaction")
```

Plot F1, HealthScore (eval), HealthScore (reco) and Satisfaction for all conditions
```{r}
ggplot(data=mydata, aes(x=cond, y=f1)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)
ggplot(data=mydata, aes(x=cond, y=health.score.eval)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)
ggplot(data=mydata, aes(x=cond, y=reco.health.score)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)
ggplot(data=mydata, aes(x=cond, y=satisfaction)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)
```



# Analysis 

## F1 scores

MANOVA for F1 scores
```{r}
model = lm(f1 ~ tags_mode + reco_mode + tags_mode:reco_mode, data = mydata)
print(Anova(model, type = 'II'))
```

Post hoc 
```{r}
lsmeans(model,
        pairwise ~ reco_mode,
        adjust="bonferroni")
```

### When Tags-Mode = no-tags, cheking for main effect of Reco-Mode
ANOVA for F1
```{r}
model_no_tags = lm(f1 ~ reco_mode, data = mydata_no_tags)
print(Anova(model_no_tags, type = 'II'))
```

### When Tags-Mode = tags, cheking for main effect of Reco-Mode
ANOVA for F1s
```{r}
model_tags = lm(f1 ~ reco_mode, data = mydata_tags)
print(Anova(model_tags, type = 'II'))
```

## Health Scores (eval)

MANOVA for health scores (eval)
```{r}
model = lm(health.score.eval ~ tags_mode + reco_mode + tags_mode:reco_mode, data = mydata)
print(Anova(model, type = 'II'))
```

## Satisfaction

ANOVA for satisfaction
```{r}
model = lm(satisfaction ~ tags_mode + reco_mode + tags_mode:reco_mode, data = mydata)
print(Anova(model, type = 'II'))
```

## Easiness

ANOVA for easiness
```{r}
model = lm(easiness ~ tags_mode + reco_mode + tags_mode:reco_mode, data = mydata)
print(Anova(model, type = 'II'))
```


# Interaction plot

```{r}
interaction.plot(x.factor     = mydata$tags_mode,
                 trace.factor = mydata$reco_mode,
                 response     = mydata$f1,
                 fun = mean,
                 type="b",
                 col=c("black","red","green"),  ##  Colors for levels of trace var.
                 pch=c(19, 17, 15),             ##  Symbols for levels of trace var.
                 fixed=TRUE,                    ##  Order by factor order in mydata
                 leg.bty = "o",
                 xlab = "Reco-Mode",
                 ylab = "F1",
                 #ylim = c(3.7,4.9),
                 trace.label = "Tag-Mode")


interaction.plot(x.factor     = mydata$tags_mode,
                 trace.factor = mydata$reco_mode,
                 response     = mydata$health.score.eval,
                 fun = mean,
                 type="b",
                 col=c("black","red","green"),  ##  Colors for levels of trace var.
                 pch=c(19, 17, 15),             ##  Symbols for levels of trace var.
                 fixed=TRUE,                    ##  Order by factor order in mydata
                 leg.bty = "o",
                 xlab = "Reco-Mode",
                 ylab = "Health Score Eval",
                 #ylim = c(3.7,4.9),
                 trace.label = "Tag-Mode")

interaction.plot(x.factor     = mydata$tags_mode,
                 trace.factor = mydata$reco_mode,
                 response     = mydata$satisfaction,
                 fun = mean,
                 type="b",
                 col=c("black","red","green"),  ##  Colors for levels of trace var.
                 pch=c(19, 17, 15),             ##  Symbols for levels of trace var.
                 fixed=TRUE,                    ##  Order by factor order in mydata
                 leg.bty = "o",
                 xlab = "Reco-Mode",
                 ylab = "Satisfaction",
                 #ylim = c(3.7,4.9),
                 trace.label = "Tag-Mode")

interaction.plot(x.factor     = mydata$tags_mode,
                 trace.factor = mydata$reco_mode,
                 response     = mydata$easiness,
                 fun = mean,
                 type="b",
                 col=c("black","red","green"),  ##  Colors for levels of trace var.
                 pch=c(19, 17, 15),             ##  Symbols for levels of trace var.
                 fixed=TRUE,                    ##  Order by factor order in mydata
                 leg.bty = "o",
                 xlab = "Reco-Mode",
                 ylab = "Easiness",
                 #ylim = c(3.7,4.9),
                 trace.label = "Tag-Mode")
```


# Other influences?

## Healthiness data

Is self-reported score of healthiness correlated with Esther&Larry's healthiness score?
```{r}
cor(mydata$healthy_food_num, mydata$normed.healthiness.habits, method = c("pearson", "kendall", "spearman"))
```

Is any of the healthiness data correlated with health score eval?
```{r}
cor(mydata$health.score.eval, mydata$normed.healthiness.habits, method = c("pearson", "kendall", "spearman"))
cor(mydata$health.score.eval, mydata$healthy_food_num, method = c("pearson", "kendall", "spearman"))
cor(mydata$health.score.eval, mydata$health_influence, method = c("pearson", "kendall", "spearman"))
```

## Investigating the I-am-influenced-by-healthiness-tag variable effects

In the tags_mode=tags condition, what happens with people who say they are influenced by healthiness info vs other people?
```{r}
model = lm(f1 ~ health_influence_str, data = df_tags)
print(Anova(model, type = 'II'))
model = lm(health.score.eval ~ health_influence_str, data = df_tags)
print(Anova(model, type = 'II'))
model = lm(satisfaction ~ health_influence_str, data = df_tags)
print(Anova(model, type = 'II'))
model = lm(easiness ~ health_influence_str, data = df_tags)
print(Anova(model, type = 'II'))

#model = lm(health.score.eval ~ tags_mode + reco_mode + health_influence_str + tags_mode:reco_mode + tags_mode:health_influence_str + reco_mode:health_influence_str, data = mydata)
#print(Anova(model, type = 'II'))
```

Plot dependant variables eval for people who say they are influenced by healthiness info vs other people
```{r}
ggplot(data=df_tags, aes(x=health_influence_str, y=f1)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)
ggplot(data=df_tags, aes(x=health_influence_str, y=health.score.eval)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)
ggplot(data=df_tags, aes(x=health_influence_str, y=satisfaction)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)
ggplot(data=df_tags, aes(x=health_influence_str, y=easiness)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)
```

Is this I-am-influenced-by-healthiness-tag variable correlated to any demographics?
```{r}
cor(df_tags$health_influence_int, df_tags$normed.healthiness.habits, method = c("pearson", "kendall", "spearman"))
cor(df_tags$health_influence_int, df_tags$healthy_food_num, method = c("pearson", "kendall", "spearman"))
cor(df_tags$health_influence_int, df_tags$health.score.learn.pref, method = c("pearson", "kendall", "spearman"))
cor(df_tags$health_influence_int, df_tags$health_important_int, method = c("pearson", "kendall", "spearman"))
cor(df_tags$health_influence_int, df_tags$age, method = c("pearson", "kendall", "spearman"))
cor(df_tags$health_influence_int, df_tags$education_num, method = c("pearson", "kendall", "spearman"))
cor(df_tags$health_influence_int, df_tags$employment_num, method = c("pearson", "kendall", "spearman"))
cor(df_tags$health_influence_int, df_tags$freq_cook_num, method = c("pearson", "kendall", "spearman"))
```

## Investigating the I-consider-healthiness-important-when-looking-for-a-recipe variable effects
In the tags_mode=tags condition, what happens with people who say they consider healthiness info important vs other people?
```{r}
model = lm(f1 ~ health_important_str, data = mydata)
print(Anova(model, type = 'II'))
model = lm(health.score.eval ~ health_important_str, data = mydata)
print(Anova(model, type = 'II'))
model = lm(satisfaction ~ health_important_str, data = mydata)
print(Anova(model, type = 'II'))
model = lm(easiness ~ health_important_str, data = mydata)
print(Anova(model, type = 'II'))

#model = lm(health.score.eval ~ tags_mode + reco_mode + health_influence_str + tags_mode:reco_mode + tags_mode:health_influence_str + reco_mode:health_influence_str, data = mydata)
#print(Anova(model, type = 'II'))
```

Plot dependant variables for people who say healthiness info is important vs other people
```{r}
ggplot(data=mydata, aes(x=health_important_str, y=f1)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)
ggplot(data=mydata, aes(x=health_important_str, y=health.score.eval)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)
ggplot(data=mydata, aes(x=health_important_str, y=satisfaction)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)
ggplot(data=mydata, aes(x=health_important_str, y=easiness)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)
```

```{r}
ggplot(data=df_tags, aes(x=health_important_str, y=f1)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)
ggplot(data=df_tags, aes(x=health_important_str, y=health.score.eval)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)
ggplot(data=df_tags, aes(x=health_important_str, y=satisfaction)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)
ggplot(data=df_tags, aes(x=health_important_str, y=easiness)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)
```

## Other demographics

Any correlation of demographics variables with Health Score (eval)?
```{r}
cor(mydata$health.score.eval, mydata$age, method = c("pearson", "kendall", "spearman"))
cor(mydata$health.score.eval, mydata$education_num, method = c("pearson", "kendall", "spearman"))
cor(mydata$health.score.eval, mydata$employment_num, method = c("pearson", "kendall", "spearman"))
cor(mydata$health.score.eval, mydata$freq_cook_num, method = c("pearson", "kendall", "spearman"))
```

Any correlation of demographics variables with satisfaction?
```{r}
cor(mydata$satisfaction, mydata$age, method = c("pearson", "kendall", "spearman"))
cor(mydata$satisfaction, mydata$education_num, method = c("pearson", "kendall", "spearman"))
cor(mydata$satisfaction, mydata$employment_num, method = c("pearson", "kendall", "spearman"))
cor(mydata$satisfaction, mydata$freq_cook_num, method = c("pearson", "kendall", "spearman"))
```

Regression
```{r}
summary(lm(formula = f1 ~ freq_cook + healthy_food_num + normed.healthiness.habits + age + employment_num + gender_num + education_num, data = mydata))
```
