---
title: "Data Analysis CHI"
output:
  html_document:
    toc: true
    theme: united
---

# Set up

Set working directory and load the data
```{r ggpubr}
setwd("/Users/lucileca/Desktop/Conversational_Agent/server_side/food/resources/data_collection/CHI")
##library(ggpubr)
mydata <- read.csv("res.csv")

mydata_noexp <- subset(mydata, Explanation.mode == "no explanations")
mydata_exp <- subset(mydata, Explanation.mode == "explanations")

mydata_1recipe <- subset(mydata, Comparison.mode == "1 recipe")
mydata_2recipes <- subset(mydata, Comparison.mode == "2 recipes")
mydata_3recipes <- subset(mydata, Comparison.mode == "3 recipes")

mydata_exp_1recipe <- subset(mydata_1recipe, Explanation.mode == "explanations")
mydata_noexp_1recipe <- subset(mydata_1recipe, Explanation.mode == "no explanations")
mydata_noexp_2recipes <- subset(mydata_2recipes, Explanation.mode == "no explanations")
mydata_exp_2recipes <- subset(mydata_2recipes, Explanation.mode == "explanations")
mydata_noexp_3recipes <- subset(mydata_3recipes, Explanation.mode == "no explanations")
mydata_exp_3recipes <- subset(mydata_3recipes, Explanation.mode == "explanations")
```

Libraries
```{r}
library(ggplot2)
library(ggpubr)
library(tidyr)
library(plyr)
library(dplyr)
library(magrittr)
library(car)
library(lsmeans)
library(ggpubr)
```

Check the data
```{r}
View(mydata)
```

Number of mydata points per condition
```{r}
# aggregate(cbind(count = file.name) ~ file.name, data = mydata, FUN = function(x){NROW(x)})
cat("mydata_exp_1recipe", nrow(mydata_exp_1recipe), "\n")
cat("mydata_noexp_1recipe", nrow(mydata_noexp_1recipe), "\n")
cat("mydata_exp_2recipes", nrow(mydata_exp_2recipes), "\n")
cat("mydata_noexp_2recipes", nrow(mydata_noexp_2recipes), "\n")
cat("mydata_exp_3recipes", nrow(mydata_exp_3recipes), "\n")
cat("mydata_noexp_3recipes", nrow(mydata_noexp_3recipes), "\n")
```

# Demographics

Age
```{r}
mydata_age <- mydata["Age"]
mydata_long <- gather(mydata_age, factor_key=TRUE)
mydata_long%>% group_by(key)%>%
  summarise(mean= mean(value,na.rm=TRUE), 
            sd= sd(value,na.rm=TRUE), 
            max = max(value,na.rm=TRUE),
            min = min(value,na.rm=TRUE), 
            upperQ = quantile(value,0.75,na.rm=TRUE),
            lowerQ = quantile(value,0.25,na.rm=TRUE))
```

Number of male / female
```{r}
gender_mydata <- aggregate(cbind(count = Sex) ~ Sex, 
          data = mydata, 
          FUN = function(x){NROW(x)})

ddply(gender_mydata, .(), mutate, pct = count / sum(count) * 100)
```

Employment category
```{r}
employment_mydata <- aggregate(cbind(count = Employment.Status) ~ Employment.Status, 
          data = mydata, 
          FUN = function(x){NROW(x)})

ddply(employment_mydata, .(), mutate, pct = count / sum(count) * 100)
```

Student
```{r}
education_mydata <- aggregate(cbind(count = Student.Status) ~ Student.Status, 
          data = mydata, 
          FUN = function(x){NROW(x)})

ddply(education_mydata, .(), mutate, pct = count / sum(count) * 100)
```

First language
```{r}
tmp <- aggregate(cbind(count = First.Language) ~ First.Language, 
          data = mydata, 
          FUN = function(x){NROW(x)})

ddply(tmp, .(), mutate, pct = count / sum(count) * 100)
```

Natioanality
```{r}
tmp <- aggregate(cbind(count = Nationality) ~ Nationality, 
          data = mydata, 
          FUN = function(x){NROW(x)})

ddply(tmp, .(), mutate, pct = count / sum(count) * 100)
```

CA familiarity
```{r}
tmp <- aggregate(cbind(count = CA.familiarity) ~ CA.familiarity, 
          data = mydata, 
          FUN = function(x){NROW(x)})

ddply(tmp, .(), mutate, pct = count / sum(count) * 100)
```

# Recommendations -- health scores of recipes

## Healthier recipe
Mean of healthier recipe health score
```{r}
mean(mydata$r.healthier.healthscore)
```

Mean of healthier recipe health score per condition
```{r}
cat("mydata_exp_1recipe", mean(mydata_exp_1recipe$r.healthier.healthscore), "\n")
cat("mydata_noexp_1recipe", mean(mydata_noexp_1recipe$r.healthier.healthscore), "\n")
cat("mydata_exp_2recipes", mean(mydata_exp_2recipes$r.healthier.healthscore), "\n")
cat("mydata_noexp_2recipes", mean(mydata_noexp_2recipes$r.healthier.healthscore), "\n")
cat("mydata_exp_3recipes", mean(mydata_exp_3recipes$r.healthier.healthscore), "\n")
cat("mydata_noexp_3recipes", mean(mydata_noexp_3recipes$r.healthier.healthscore), "\n")
```

Is the difference between conditions significative?
```{r}
model = lm(r.healthier.healthscore ~ Explanation.mode + Comparison.mode + Explanation.mode:Comparison.mode, data = mydata)
print(Anova(model, type = 'II'))
```

## Pref recipe

Mean of pref recipe health score
```{r}
mean(mydata$r.pref.healthscore, na.rm=TRUE)
```

Mean of pref recipe health score per condition
```{r}
cat("mydata_exp_2recipes", mean(mydata_exp_2recipes$r.pref.healthscore), "\n")
cat("mydata_noexp_2recipes", mean(mydata_noexp_2recipes$r.pref.healthscore), "\n")
cat("mydata_exp_3recipes", mean(mydata_exp_3recipes$r.pref.healthscore), "\n")
cat("mydata_noexp_3recipes", mean(mydata_noexp_3recipes$r.pref.healthscore), "\n")
```

Is the difference between conditions significative?
```{r}
model = lm(r.pref.healthscore ~ Explanation.mode + Comparison.mode + Explanation.mode:Comparison.mode, data = mydata)
print(Anova(model, type = 'II'))
```

## Decoy recipe

Mean of pref recipe health score
```{r}
mean(mydata$r.decoy.healthscore, na.rm=TRUE)
```

Mean of pref recipe health score per condition
```{r}
cat("mydata_exp_3recipes", mean(mydata_exp_3recipes$r.decoy.healthscore), "\n")
cat("mydata_noexp_3recipes", mean(mydata_noexp_3recipes$r.decoy.healthscore), "\n")
```

Is the difference between conditions significative?
```{r}
model = lm(r.decoy.healthscore ~ Explanation.mode, data = mydata)
print(Anova(model, type = 'II'))
```

# Recommendations -- utility of recipes

## Healthier recipe
Mean of healthier recipe utility
```{r}
mean(mydata$r.healthier.utility)
```

Mean of healthier recipe utility per condition
```{r}
cat("mydata_exp_1recipe", mean(mydata_exp_1recipe$r.healthier.utility), "\n")
cat("mydata_noexp_1recipe", mean(mydata_noexp_1recipe$r.healthier.utility), "\n")
cat("mydata_exp_2recipes", mean(mydata_exp_2recipes$r.healthier.utility), "\n")
cat("mydata_noexp_2recipes", mean(mydata_noexp_2recipes$r.healthier.utility), "\n")
cat("mydata_exp_3recipes", mean(mydata_exp_3recipes$r.healthier.utility), "\n")
cat("mydata_noexp_3recipes", mean(mydata_noexp_3recipes$r.healthier.utility), "\n")
```

Is the difference between conditions significative?
```{r}
model = lm(r.healthier.utility ~ Explanation.mode + Comparison.mode + Explanation.mode:Comparison.mode, data = mydata)
print(Anova(model, type = 'II'))
```

## Pref recipe

Mean of pref recipe utility
```{r}
mean(mydata$r.pref.utility, na.rm=TRUE)
```

Mean of pref recipe utility per condition
```{r}
cat("mydata_exp_2recipes", mean(mydata_exp_2recipes$r.pref.utility), "\n")
cat("mydata_noexp_2recipes", mean(mydata_noexp_2recipes$r.pref.utility), "\n")
cat("mydata_exp_3recipes", mean(mydata_exp_3recipes$r.pref.utility), "\n")
cat("mydata_noexp_3recipes", mean(mydata_noexp_3recipes$r.pref.utility), "\n")
```

Is the difference between conditions significative?
```{r}
model = lm(r.pref.utility ~ Explanation.mode + Comparison.mode + Explanation.mode:Comparison.mode, data = mydata)
print(Anova(model, type = 'II'))
```

## Decoy recipe

Mean of pref recipe utility
```{r}
mean(mydata$r.decoy.utility, na.rm=TRUE)
```

Mean of pref recipe utility per condition
```{r}
cat("mydata_exp_3recipes", mean(mydata_exp_3recipes$r.decoy.utility), "\n")
cat("mydata_noexp_3recipes", mean(mydata_noexp_3recipes$r.decoy.utility), "\n")
```

Is the difference between conditions significative?
```{r}
model = lm(r.decoy.utility ~ Explanation.mode, data = mydata)
print(Anova(model, type = 'II'))
```

# Recipe choice

## Recipe choice per condition

```{r}
mydata_noexp_1recipe_chosen <- aggregate(cbind(count = chosen) ~ chosen, 
          data = mydata_noexp_1recipe, 
          FUN = function(x){NROW(x)})
ddply(mydata_noexp_1recipe_chosen, .(), mutate, pct = count / sum(count) * 100)

mydata_exp_1recipe_chosen <- aggregate(cbind(count = chosen) ~ chosen, 
          data = mydata_exp_1recipe, 
          FUN = function(x){NROW(x)})
ddply(mydata_exp_1recipe_chosen, .(), mutate, pct = count / sum(count) * 100)

mydata_noexp_2recipes_chosen <- aggregate(cbind(count = chosen) ~ chosen, 
          data = mydata_noexp_2recipes, 
          FUN = function(x){NROW(x)})
ddply(mydata_noexp_2recipes_chosen, .(), mutate, pct = count / sum(count) * 100)

mydata_exp_2recipes_chosen <- aggregate(cbind(count = chosen) ~ chosen, 
          data = mydata_exp_2recipes, 
          FUN = function(x){NROW(x)})
ddply(mydata_exp_2recipes_chosen, .(), mutate, pct = count / sum(count) * 100)

mydata_noexp_3recipes_chosen <- aggregate(cbind(count = chosen) ~ chosen, 
          data = mydata_noexp_3recipes, 
          FUN = function(x){NROW(x)})
ddply(mydata_noexp_3recipes_chosen, .(), mutate, pct = count / sum(count) * 100)

mydata_exp_3recipes_chosen <- aggregate(cbind(count = chosen) ~ chosen, 
          data = mydata_exp_3recipes, 
          FUN = function(x){NROW(x)})
ddply(mydata_exp_3recipes_chosen, .(), mutate, pct = count / sum(count) * 100)
```

## Recipe choice per Comparison-Mode

```{r}
mydata_1recipe_chosen <- aggregate(cbind(count = chosen) ~ chosen, 
          data = mydata_1recipe, 
          FUN = function(x){NROW(x)})
ddply(mydata_1recipe_chosen, .(), mutate, pct = count / sum(count) * 100)

mydata_2recipes_chosen <- aggregate(cbind(count = chosen) ~ chosen, 
          data = mydata_2recipes, 
          FUN = function(x){NROW(x)})
ddply(mydata_2recipes_chosen, .(), mutate, pct = count / sum(count) * 100)

mydata_3recipes_chosen <- aggregate(cbind(count = chosen) ~ chosen, 
          data = mydata_3recipes, 
          FUN = function(x){NROW(x)})
ddply(mydata_3recipes_chosen, .(), mutate, pct = count / sum(count) * 100)
```

## Recipe choice per Explanation-Mode

```{r}
mydata_exp_chosen <- aggregate(cbind(count = chosen) ~ chosen, 
          data = mydata_exp, 
          FUN = function(x){NROW(x)})
ddply(mydata_exp_chosen, .(), mutate, pct = count / sum(count) * 100)

mydata_noexp_chosen <- aggregate(cbind(count = chosen) ~ chosen, 
          data = mydata_noexp, 
          FUN = function(x){NROW(x)})
ddply(mydata_noexp_chosen, .(), mutate, pct = count / sum(count) * 100)
```

# Plots

## Plots per condition
```{r}
ggplot(data=mydata, aes(x=file.name, y=chosen.r.healthy)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)

ggplot(data=mydata, aes(x=file.name, y=small.talk)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)

ggplot(data=mydata, aes(x=file.name, y=self.disclosures)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)

ggplot(data=mydata, aes(x=file.name, y=feedback)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)

ggplot(data=mydata, aes(x=file.name, y=usefulness)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)

ggplot(data=mydata, aes(x=file.name, y=transparency)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)

ggplot(data=mydata, aes(x=file.name, y=ease.of.use)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)

ggplot(data=mydata, aes(x=file.name, y=authority)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)

ggplot(data=mydata, aes(x=file.name, y=liking)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)

ggplot(data=mydata, aes(x=file.name, y=trust)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)

ggplot(data=mydata, aes(x=file.name, y=satisfaction)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)

ggplot(data=mydata, aes(x=file.name, y=intention.to.cook)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)

ggplot(data=mydata, aes(x=file.name, y=intention.of.use)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)

ggplot(data=mydata, aes(x=file.name, y=recommendation.accuracy)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)
```

## Plots per Comparison-Mode
```{r}
ggplot(data=mydata, aes(x=Comparison.mode, y=chosen.r.healthy)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)

ggplot(data=mydata, aes(x=Comparison.mode, y=small.talk)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)

ggplot(data=mydata, aes(x=Comparison.mode, y=self.disclosures)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)

ggplot(data=mydata, aes(x=Comparison.mode, y=feedback)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)

ggplot(data=mydata, aes(x=Comparison.mode, y=usefulness)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)

ggplot(data=mydata, aes(x=Comparison.mode, y=transparency)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)

ggplot(data=mydata, aes(x=Comparison.mode, y=ease.of.use)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)

ggplot(data=mydata, aes(x=Comparison.mode, y=authority)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)

ggplot(data=mydata, aes(x=Comparison.mode, y=liking)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)

ggplot(data=mydata, aes(x=Comparison.mode, y=trust)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)

ggplot(data=mydata, aes(x=Comparison.mode, y=satisfaction)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)

ggplot(data=mydata, aes(x=Comparison.mode, y=intention.to.cook)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)

ggplot(data=mydata, aes(x=Comparison.mode, y=intention.of.use)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)

ggplot(data=mydata, aes(x=Comparison.mode, y=recommendation.accuracy)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)
```


## Plots per Explanation-Mode
```{r}
ggplot(data=mydata, aes(x=Explanation.mode, y=chosen.r.healthy)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)

ggplot(data=mydata, aes(x=Explanation.mode, y=small.talk)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)

ggplot(data=mydata, aes(x=Explanation.mode, y=self.disclosures)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)

ggplot(data=mydata, aes(x=Explanation.mode, y=feedback)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)

ggplot(data=mydata, aes(x=Explanation.mode, y=usefulness)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)

ggplot(data=mydata, aes(x=Explanation.mode, y=transparency)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)

ggplot(data=mydata, aes(x=Explanation.mode, y=ease.of.use)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)

ggplot(data=mydata, aes(x=Explanation.mode, y=authority)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)

ggplot(data=mydata, aes(x=Explanation.mode, y=liking)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)

ggplot(data=mydata, aes(x=Explanation.mode, y=trust)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)

ggplot(data=mydata, aes(x=Explanation.mode, y=satisfaction)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)

ggplot(data=mydata, aes(x=Explanation.mode, y=intention.to.cook)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)

ggplot(data=mydata, aes(x=Explanation.mode, y=intention.of.use)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)

ggplot(data=mydata, aes(x=Explanation.mode, y=recommendation.accuracy)) + geom_boxplot() + stat_summary(fun.y=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE)
```


# ANOVAs 

```{r}
model = lm(chosen.r.healthy ~ Explanation.mode + Comparison.mode + Explanation.mode:Comparison.mode, data = mydata)
print(Anova(model, type = 'II'))

model = lm(small.talk ~ Explanation.mode + Comparison.mode + Explanation.mode:Comparison.mode, data = mydata)
print(Anova(model, type = 'II'))

model = lm(self.disclosures ~ Explanation.mode + Comparison.mode + Explanation.mode:Comparison.mode, data = mydata)
print(Anova(model, type = 'II'))

model = lm(feedback ~ Explanation.mode + Comparison.mode + Explanation.mode:Comparison.mode, data = mydata)
print(Anova(model, type = 'II'))

model = lm(usefulness ~ Explanation.mode + Comparison.mode + Explanation.mode:Comparison.mode, data = mydata)
print(Anova(model, type = 'II'))

model = lm(transparency ~ Explanation.mode + Comparison.mode + Explanation.mode:Comparison.mode, data = mydata)
print(Anova(model, type = 'II'))

model = lm(ease.of.use ~ Explanation.mode + Comparison.mode + Explanation.mode:Comparison.mode, data = mydata)
print(Anova(model, type = 'II'))

model = lm(authority ~ Explanation.mode + Comparison.mode + Explanation.mode:Comparison.mode, data = mydata)
print(Anova(model, type = 'II'))

model = lm(liking ~ Explanation.mode + Comparison.mode + Explanation.mode:Comparison.mode, data = mydata)
print(Anova(model, type = 'II'))

model = lm(trust ~ Explanation.mode + Comparison.mode + Explanation.mode:Comparison.mode, data = mydata)
print(Anova(model, type = 'II'))

model = lm(satisfaction ~ Explanation.mode + Comparison.mode + Explanation.mode:Comparison.mode, data = mydata)
print(Anova(model, type = 'II'))

model = lm(intention.to.cook ~ Explanation.mode + Comparison.mode + Explanation.mode:Comparison.mode, data = mydata)
print(Anova(model, type = 'II'))

model = lm(intention.of.use ~ Explanation.mode + Comparison.mode + Explanation.mode:Comparison.mode, data = mydata)

model = lm(recommendation.accuracy ~ Explanation.mode + Comparison.mode + Explanation.mode:Comparison.mode, data = mydata)
print(Anova(model, type = 'II'))
print(Anova(model, type = 'II'))
```